### 2025-09-01 LabelStyles/skeleton-maps.tex
map example

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[paperheight=4in,paperwidth=4in,margin=0.1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\pagenumbering{gobble}
\usepackage{setspace}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\begin{center}
\textbf{\Large Custom Fonts}
\end{center}
\begin{flushright}
\uppercase{Apiaceae}
\end{flushright}

\noindent

\begin{minipage}[t]{0.78\textwidth}\vspace*{0pt}

\begingroup
\large
*Lomatium nevadense* (S. Watson) J.M. Coult. & Rose     
Fide: *Intermountain Flora*, det.: RCB, 29 Aug, 2023.
\normalsize
\endgroup

@@

\begingroup
U.S.A., Nevada, Washoe Co., 17N 20E 19. Washoe Summit. 39.32677 -119.78537 (WGS84 5m).

Granitoid derived aeolian loamy sand soils. At 5,200 ft, on a slope, 4° slo. 57° asp.; geology: Igneous and Sedimentary, undifferentiated.  
Veg.: *Artemisia tridentata* var. *wyomimgensis, Poa secunda, Agropyron cristatum, Achnatherum thurberianum, Purshia tridenata*. Ass.: *Bromus tectorum, Phlox longifolia*.

@@

\vspace*{\fill}
\begingroup
Reed Clark Benkendorf 2823; 6 May, 2023
\endgroup
\end{minipage}

\% \hfill

\begin{minipage}[c]{0.18\textwidth}\vspace*{0pt}
\hspace*{4mm}% left margin
\centering
\includegraphics[width=\linewidth,height=0.66\textheight,keepaspectratio]{~/Documents/assoRted/Barneby_Lives_dev/LabelStyles/map_2823.png}
\end{minipage}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[paperheight=4in,paperwidth=4in,margin=0.1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\pagenumbering{gobble}
\usepackage{setspace}
\usepackage{wrapfig}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\begin{center}
\textbf{\Large Label with Map}
\end{center}
\begin{flushright}
\uppercase{Apiaceae}
\end{flushright}

\begingroup
\large

\emph{Lomatium nevadense} (S. Watson) J.M. Coult. \& Rose\\
\normalsize Fide: \emph{Intermountain Flora}, det.: RCB, 29 Aug, 2023.
\endgroup

\begin{wrapfigure}[5]{r}[0pt]{1in} % wrap text around fig, [5] lines of text,
% {r} align, [0pt] no additional spacing, {1in} image
\vspace{-5.0ex} % push the image upwards above it's starting line. 
\includegraphics[width=1in,height=1in,keepaspectratio]{~/Documents/assoRted/Barneby_Lives_dev/LabelStyles/maps/map_2823.png} % path to image
\end{wrapfigure}

@@

\begingroup

U.S.A., Nevada, Washoe Co., 17N 20E 19. Washoe Summit. 39.32677
-119.78537 (WGS84 5m).

Granitoid derived aeolian loamy sand soils. At 5,200 ft, on a slope, 4°
slo. 57° asp.; geology: Igneous and Sedimentary, undifferentiated.

\par

Veg.: \emph{Artemisia tridentata} var. \emph{wyomimgensis, Poa secunda,
Agropyron cristatum, Achnatherum thurberianum, Purshia tridenata}. Ass.:
\emph{Bromus tectorum, Phlox longifolia}.

@@

\vspace*{\fill}
\begingroup

Reed Clark Benkendorf 2823; 6 May, 2023 \endgroup
